\problemname{Initials}


When marking computer science assignments, markers like to mark each
student in order of how they are listed in class. The way the class is
listed is quite strange though, a class is sorted by concatenating the
first name to the last name (for example Harry Potter becomes
PotterHarry) and all upper case letters are turned to lower case. Then
sorting those strings lexicographically is the order of the
class. Each student needs a Unix directory for the marker to put their
assignments in.

Since the marker is lazy, he decides to create a directory for each
student only using their initials (first letter of last name followed
by the first letter of first name). The marker soon realizes that the
way Unix sorts the directories, students are no longer sorted in the
correct order and there are now duplicate folder names. Oh no! This
must be fixed.

For each name, we are allowed to add $0$ or more letters from the
original name to the initials, except you must always use the first
$k$ unchosen letters in the initials. For example, the initials of
Harry Potter are PH. Adding $2$ letters make it PotH, adding $6$ letters
makes it PotterHa.

The markers come to you for help. Your job is to write a program which
tells the markers the minimum number of letters they need to add to
put all the students into correct sorted order, so that all resulting
``extended'' initials are unique.

For example, in the sample input below, the initials (sorted) would be
(HA, HB, ZZ).  By adding three letters we get (HaB, HatA, ZZ) which is
the correct sorted order.


\section*{Input}

The first line contains a single integer $2 \leq N \leq 1000$
indicating the number of students.  Then follow $N$ lines, each
containing two strings: the first and last name of the student.  The
first and last name each contains at least one character, and they
consist of only lowercase and uppercase English alphabetic letters.
The combined length of each student name will be at most $80$
characters.  No two students will have the same concatentated name (as
described above).

\section*{Output}

A single number on a line by itself, the minimum number of letters
that need to be added to put all the students in sorted order.
